Dynein project log

### 2016-11-18 thesis_stuff/thesis_stuff.tex

The mean speed of dynein is $134\pm 60$~nm~s$^{-1}$.

@@

\subsection{Program Scaling}
Program runtimes, as of commit 62c4d:

@@

\section{Todo}
\begin{itemize}
\item Add dt testing figure to thesis\_stuff.tex.
\item Make all figures in thesis\_stuff.tex be dependencies of thesis\_stuff.tex in the Makefile; it should be deducible to a novice how every figure is generated in code.
\item Check out kinetic parameters papers in the Winch model, see how they are aquired
\item Generate a figure explaining how our model simplifies the rate constants in the Winch paper / annual review.
\item Make a figure with PyMol visualizations with and without our model superimposed
\item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
\item Make Dynein binding rate diagram showing how our model relates to the Imamula one
\item Make pretty dynein visualization in PyMol (or some software) showing how dimerization happens AND how docking to the MT happens; ask David what this should look like
\end{itemize}
\end{document}

>>>>

The mean speed of dynein is $134\pm 60$~nm~s$^{-1}$.  It looks like
perhaps the speed should be more like 80 or 80 nm/s~\cite{reck2006single}.

@@

Note also another paper that is very similar to that of Weihong~\cite{dewitt2012cytoplasmic}.

\section{Program Scaling}
Program runtimes, as of commit 62c4d:

@@

\section{Todo}
\begin{itemize}
\item Add dt testing figure to thesis\_stuff.tex.
\item Make all figures in thesis\_stuff.tex be dependencies of thesis\_stuff.tex in the Makefile; it should be deducible to a novice how every figure is generated in code.
\item Check out kinetic parameters papers in the Winch model, see how they are aquired
\item Generate a figure explaining how our model simplifies the rate constants in the Winch paper / annual review.
\item Make a figure with PyMol visualizations with and without our model superimposed
\item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
\item Make Dynein binding rate diagram showing how our model relates to the Imamula one
\item Make pretty dynein visualization in PyMol (or some software) showing how dimerization happens AND how docking to the MT happens; ask David what this should look like
\end{itemize}

\bibliographystyle{plain}
\bibliography{thesis_stuff}

\end{document}
